%\include{packages}
%\begin{document}

\chapter{Conclusion}\label{conclusion}

The detection of lacunes in \textsc{mri} is necessary for neurological study surrounding cerebral small vessel disease and the incidence of stroke. Current identification methods are time consuming and largely inconsistent, resulting in potentially invalid research conclusions and misdiagnosis for those with a heightened risk of stroke. Lacune detection models exist and are successful in classifying lacunes, however are reliant on location-based variables. These variables must be estimated using existing tools to segment the brain structure, however these tools are not necessarily available to clinicians. 

We proposed a location-independent two-dimensional convolutional neural network model for the detection of lacunes in \textsc{mri}. Our proposed model adapts the lacune detection model by \cite{GhafoorianM.2017Dml3} and makes three major changes. The first is the removal of dependence on location-based variables. This reduces the quantity and complexity of data pre-processing, and ensures that samples are classified correctly even if they occur in less frequently observed regions.

The second adaptation is use of soft tissue extraction on the T1-weighted scans prior to model input. This process occurs to remove identification features visible in \textsc{mri}, and has the additional effect of enlarging spaces that appear similar to \textsc{csf}, and hence enlarges lacunes.

The third change is the removal of dimension reduction prior to the first convolutional layer. Early reduction of image dimension results in loss of pixel information that may contain lacunes. Maintaining the dimension of the input image ensures that vital pixel information is retained early in the model, which aids in the identification of smaller lacunes.

The final simplified lacune detection model on correlated data exhibited a testing sensitivity and specificity of 99.9\% and 99.8\% respectively. The model was consolidated after candidate generation to maintain model simplicity, and reduce computation time and data pre-processing.

With uncorrelated data, an identical model structure exhibited a testing sensitivity and specificity of respectively 55.7\% and 84.9\%. Training the model on T1-weighted data without soft tissue extraction increased the sensitivity and specificity rates respectively to 85.3\% and 92.0\%. 

\section{Improvements and further research}

Under the assumption of uncorrelated data sets, the original model exhibits a very high detection performance, however the incidence of remaining false-positive errors requires clinicians to supervise the model outputs. Each positive classification must be examined by clinicians to reduce the number of false-positives. The high specificity rate helps to restrict this number, however the dimensions of each \textsc{mri} scan are high, involving approximately 50,000 voxels within the brain tissue. Hence, further model improvement can be made to reduce the number of false-positives.

Information inherent in two-dimensional sample subimages may not contain enough context to make an accurate classification for some samples. This is particularly the case with samples that contain blood vessels or perivascular spaces that appear circular from the axial perspective. The amount of context included in the sample can be increased by considering three-dimensional samples and employing a three-dimensional \textsc{cnn}. The inclusion of volume based samples ensures that a distinction can be made between structures that only appear circular in the two-dimensional patches, and samples that are truly spherical. It should be noted that three-dimensional \textsc{cnn}s require a large number of weights and hence have lengthy computation time if applied to all points in a volume. Implementation time can be improved by applying the three-dimensional \textsc{cnn} to the candidate lacunes indicated by the initial two-dimensional \textsc{cnn} as a form of false-positive reduction.

Soft tissue extraction applied to the T1-weighted scans resulted in very distinct edges between the brain matter and surrounding structures. This resulted in the masking of voxels that exhibited a high probability of \textsc{csf} content, which includes lacunes. Additional research could be conducted on the impact of soft tissue extraction on lacune detection. If found to be detrimental to model performance, it may be beneficial to implement lacune detection on T1-weighted scans prior to soft tissue extraction.

Once the sensitivity and specificity rates of the correlation corrected model is improved, the algorithm is to be included as part of the Sydney MAS \textsc{mri} data processing pipeline. Inclusion of an improved model will assist neuroscientists in the efficient and consistent detection of lacunes, and thus ensure the validity of medical studies conducted. Additionally, the inclusion of a model during medical practice would provide accurate detection of lacunes in the \textsc{mri} of individual patients, indicating any heightened risk of stroke. The awareness of any increased risk could then result in appropriate treatment and possible avoidance of stroke.

Recent attention has been drawn to other forms of automated medical diagnosis. Algorithms have been found successful in the detection of breast cancer \citep{LiuYun2018} and bone fractures \citep{Lindsey2018}. The structure of data in these contexts is similar to the three-dimensional array structure of \textsc{mri}, hence the \textsc{cnn} techniques applied can be extended to other medical classification and diagnostic tasks.
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\include{bibliography}
%\end{document}