\beforepreface

%\afterpage{\blankpage}
%\blankpage
% plagiarism

\prefacesection{Plagiarism statement}

\vskip 10pc \noindent I declare that this thesis is my
own work, except where acknowledged, and has not been submitted for
academic credit elsewhere. 

\vskip 2pc  \noindent I acknowledge that the assessor of this
thesis may, for the purpose of assessing it:
\begin{itemize}
\item Reproduce it and provide a copy to another member of the University; and/or,
\item Communicate a copy of it to a plagiarism checking service (which may then retain a copy of it on its database for the purpose of future plagiarism checking).
\end{itemize}

\vskip 2pc \noindent I certify that I have read and understood the University Rules in
respect of Student Academic Misconduct, and am aware of any potential plagiarism penalties which may 
apply.\vspace{24pt}

\vskip 2pc \noindent By signing this declaration I am agreeing to the statements and conditions above.
\vskip 2pc
Signed: \rule{7cm}{0.25pt} \hfill Date: \rule{4cm}{0.25pt}

%\afterpage{\blankpage}
\afterpage{\cleardoublepage}

% Acknowledgements are optional


\prefacesection{Acknowledgements}

\bigskip I would like to thank my supervisors, Pierre and Wei, for their guidance and support throughout this year.

\bigskip\noindent Thanks to Jiyang for all your assistance and helping with data preparation.

\bigskip\noindent I would also like to thank Ramanan, Jeffrey, and Prosha for giving me helpful advice and endless proof-reading.

\bigskip\noindent Thanks also to my parents and Kevin for looking after me over the past year.

\bigskip\bigskip\bigskip\noindent Melinda Mortimer, 26 October 2018.

%{\bigskip}By far the greatest thanks must go to my supervisor for
%the guidance, care and support they provided. 
%
%{\bigskip\noindent}Thanks must also go to Emily, Michelle, John and Alex who helped by
%proof-reading the document in the final stages of preparation.
%
%{\bigskip\noindent}Although I have not lived with them for a number of years, my family also deserve many thanks for their encouragement.
%
%{\bigskip\noindent} Thanks go to Robert Taggart for allowing his thesis style to be shamelessly copied.
%
%{\bigskip\bigskip\bigskip\noindent} Fred Flintstone, 2 November 2015.

%\afterpage{\blankpage}
\afterpage{\cleardoublepage}

% Abstract

\prefacesection{Abstract}

Cerebral small vessel disease is a neurological disease that affects over 90\% of elderly and is a major cause of stroke, dementia, and cognitive decline. Biomarkers of the disease are visible in \textsc{mri} and are manually identified by trained clinicians. Lacunes are one such biomarker and are of particular interest for their potential role in the advancement of cerebral small vessel disease and in the incidence of stroke. However, the manual identification of lacunes is difficult, laborious, and largely inconsistent.

In this thesis, we present a convolutional neural networks model for the automated detection of lacunes in \textsc{mri}. The model adapts an existing model by \cite{GhafoorianM.2017Dml3} to the scenario in which location-based variables are unavailable. In particular, we remove the dependence on location-based variables, perform extraction of the brain matter prior to model input, and remove early dimension reduction. The resulting model exhibited a testing sensitivity of 99.9\% and a specificity of 99.8\%.

It should be noted that this model performance was a result of sampling correlations between the training, testing, and validation sets. A discussion of the final results and the corrected model is provided.

%\afterpage{\blankpage}
